Proposed Solution

### 2016-01-29 intro1.tex

Configuration errors are one of the most important root-causes of 
modern software system failures~\cite{xu15systems,yin11anempirical}. 
In practice, misconfiguration problems may result in 
security vulnerabilities,
application crashes, severe disruptions in software functionality,
and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.
Although several tools have been proposed to automate configuration
error diagnosis after failures occur%
~\cite{wang04automatic,attariyan10automating,%
su07autobash,whitaker04configuration}, 
these tools rely on manual ways to understand and detect the failure symptoms. The main reason for this approach ... \ruzica{Ennan, can you talk here how usually config files look, only untyped assigments}

>>>>

Configuration errors are one of the most important root-causes of 
modern software system failures~\cite{xu15systems,yin11anempirical}. 
In practice, misconfiguration problems may result in 
security vulnerabilities,
application crashes, severe disruptions in software functionality,
and incorrect program executions%
~\cite{xu15systems,zhang14encore,yuan11context}.
Although several tools have been proposed to automate configuration
error diagnosis after failures occur%
~\cite{wang04automatic,attariyan10automating,%
su07autobash,whitaker04configuration}, 
these tools rely on manual ways to understand and detect the failure 
symptoms. The main reasons are:
1) entries in configuration files are untyped assignments, 
2) there is no explicit structure policy for the entries in 
configuration files, and 3) there is surprisingly little rules 
specifying the entries' constraints.

### 2016-01-29 motiv1.tex

\begin{figure}[t] \centering
\includegraphics[width=0.98\textwidth]{figs/example}
\caption{Motivating examples. Our target configuration errors are
  classified into five groups. The five examples here correspond to
  these groups, respectively.}
\label{fig-example}
\end{figure}

@@

>>>>

\subsection{Entry Missing Errors}

When the user wants to use OpenLDAP to enable her directory access
protocol, she need to use the password policy overlay, so she may need
to write the following entries in her OpenLDAP configuration file:\\
\texttt{
 \hspace*{3em}overlay ppolicy\\}
However, this configuration makes LDAP server fail to work.
Running \app on this configuration file returns:
\xxx{Mark, put results here}\\
This was the source of the error. When using the password policy overlay
in OpenLDAP, we have to first include the related schema before the
{\tt overlay ppolicy}. Namely, the correct configuration should be:\\
\texttt{
 \hspace*{3em}include schema/ppolicy.schema\\
 \hspace*{3em}overlay ppolicy\\
}

\subsection{Value Type Errors}

When the user tries to install MySQL, she needs to initiate the path for
log information generated by MySQL. A user put the following code in 
her MySQL configuration file:\\
\texttt{
 \hspace*{3em}general\_log = /var/log/mysql/mysql.log\\}
Unfortunately, the log information cannot be correctly written.
Running \app on this configuration file returns:
\xxx{Mark, put results here}\\
This is the root-cause of this misconfiguration problem. 
The entry ``general\_log'' should be an integer, 
rather than string. In MySQL, there is another entry named
``general\_log\_file'' used to specify the log path.

\subsection{Value Correlation Errors}

When configuring PHP on MySQL, the user writes the following lines 
of entries in her both PHP and MySQL configuration files:\\
\texttt{
 \hspace*{3em}mysql's config\\
 \hspace*{3em}max\_connections = 300\\
 \hspace*{3em}...\\
 \hspace*{3em}php's config\\
 \hspace*{3em}mysql.max\_persistent = 400\\}
Unfortunately, the MySQL outputs the error information:
``too many connections''.
Running \app on this combined configuration file returns:
\xxx{Mark, put results here}\\
This is the root-cause of the problem.
In particular, the ``mysql.max\_persistent'' in PHP should be no
larger than the ``max\_connections'' in MySQL configuration file.

\subsection{Format Errors}
\xxx{I am not sure if we still need the format error, so I 
put it the last one.}

When configuring NetApp commercial storage system, 
the user writes the following entry:\\
\texttt{
 \hspace*{3em}InitiatorName: iqn:DEV\_DOMAIN\\
} 
The NetApp storage share cannot be recognized. 
Thus, we run \app on this configuration file and get the results:
\xxx{Mark, put results here}\\
This is the root-cause of the problem,
since the iscsi device's initiator name, \ie, InitiatorName,
only allows lowercase letters. However, the user sets the name with
capital letters ``DEV\_DOMAIN''.

\com{
\begin{figure}[t] \centering
\includegraphics[width=0.98\textwidth]{figs/example}
\caption{Motivating examples. Our target configuration errors are
  classified into five groups. The five examples here correspond to
  these groups, respectively.}
\label{fig-example}
\end{figure}

@@

}
